class: bg-main1 split-30 hide-slide-number

.column.bg-main3[
]
.column.slide-in-right[
.sliderbox.bg-main2.vmiddle[
.font3[HowTo - Dockerfile and Docker Compose]
]]

---

class: middle center bg-main1 hide-slide-number

# Dockerfile

--
  ## Dockerfile is a simple text file with a set of commands and instructions that the developer defines to build an image.
  
--
```{r echo = T, eval = F}

FROM rocker/shiny:3.5.3 # Base image

RUN R -e "install.packages('dplyr')" # Actions to be done by the container 

COPY apps/. /srv/shiny-server/ # File copy from the source to the container
  
```

---

class: middle center bg-main1 hide-slide-number

# Docker-Compose

--
  ## Docker-Compose is a tool used to build a solution that leverages multiple containers at once.
  ## The necessary services are defined at the `docker-compose.yaml` file, in order to allow the solution to run in an isolated environment.
  
---

class: middle center bg-main1 hide-slide-number

# Docker-Compose

```{r echo = T, eval = F}
version: "3"

services:
  shiny:
    image: lhzpaese/shiny:3.5.3
    container_name: shiny_server
    ports:
      - "3838:3838"
  rstudio:
    image: lhzpaese/rstudio:3.5.3
    container_name: rstudio_server
    ports:
      - "8787:8787"
```

---

class: middle center bg-main1 hide-slide-number

# DockerHUB

--

  ## Docker Hub is a cloud-based repository where Docker users an create, test, store and distribute built images of their containers.
  ## It allows the creation of images from .text-hl[GitHub] `r icons::fontawesome("github")` repositories, building new versions at every commit from the developers.
  
---